---
title: "Appendix C"
output:
  pdf_document: 
    number_sections: true
  html_notebook: default
header-includes:
  - \usepackage{booktabs}
---

This appendix aims to illustrate the process of calibrating a disaggregated
SEIR model to the 1957 Flu data via Hamiltonian Monte Carlo. We assess the 
results by exploring trace plots, estimates for the basic reproduction 
number ($R_0$) and the scaled WAIFW matrix.

\tableofcontents 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      cache = TRUE)

## WORKAROUND: https://github.com/rstudio/rstudio/issues/6692
## Revert to 'sequential' setup of PSOCK cluster in RStudio Console on macOS and R 4.0.0
if (Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) && 
    Sys.info()["sysname"] == "Darwin" && getRversion() == "4.0.0") {
  parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
}

library(bayesplot)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(Metrics)
library(purrr)
library(readr)
library(readsdr)
library(scales)
library(stringr)
library(tidyr)

source("./R/Metrics.R")
```

\newpage

# 1957 Flu Data

```{r}
raw_data <- read_csv("./data/flu_data_1957.csv") %>% 
  mutate(time = row_number() - 1,
         week = dmy(week))

n_weeks <- nrow(raw_data)

# First week correspond to initial values
length_data <- n_weeks - 1

flu_data <- raw_data %>% pivot_longer(c(-week, - time), 
                                      names_to = "cohort",
                                      values_to = "y")

age_groups <- unique(flu_data$cohort)

pop_df <- data.frame(age_group  = age_groups,
                     population = c(949, 1690, 3467, 1894)) %>% 
  mutate(proportion = population / sum(population))

ggplot(flu_data, aes(x = week, y = y)) +
  geom_col(fill = "steelblue") +
  facet_wrap(~ cohort) +
  theme_pubr() +
  labs(y = "Incidence")
```

# Calibration

## Biological parameters

* Latent period ($\sigma^{-1}$): 1 day. It is the inverse of the rate of 
onset of infectiousness.

* Infectious period ($\gamma^{-1}$): 2 days. It is the inverse of the recovery
rate.

## Priors

* Normalised transmission rates: $k_{ij} \sim normal(0, 10)$
* Reporting fraction: $\rho \sim normal(0.5, 0.5)$

## HMC

```{r}
mdl_file <- "./deterministic_models/4_cohorts_SEIR_matrix_sym.stmx"

n_cohorts <- 4

stock_names  <- paste0(c("S", "E", "I", "R", "C"), rep(1:n_cohorts, each = 5))
stock_matrix <- matrix(0, nrow = 1, ncol = length(stock_names))
stock_names  -> colnames(stock_matrix)
stock_df     <- as.data.frame(stock_matrix)

infected_cohorts <- 3:4
infected_value   <- 1

for(i in seq_len(n_cohorts)) {
  S_stock <- paste0("S", i)
  S_val   <- pop_df[i, "population"]
  
  if(i %in% infected_cohorts) {
    I_stock <- paste0("I", i)
    C_stock <- paste0("C", i)
    stock_df[, I_stock] <- infected_value
    stock_df[, C_stock] <- infected_value
    S_val   <- S_val - infected_value
  }
  stock_df[, S_stock] <- S_val
}

pop_size   <- sum(pop_df$population)
stock_list <- as.list(stock_df)
const_list <- list(recovery_time = 1.5 / 7,
                   latent_period = 1.5 / 7,
                   population    = pop_size)

mdl <- read_xmile(mdl_file, stock_list, const_list)

start_time <- 0
stop_time  <- n_weeks - 1
```

```{r}
source("./R/stan_utils.R")
source("./R/write_SEIR_model.R")

filename <- "./Stan_files/flu_example/flu.stan"

params_prior <- c("  params ~ normal(0, 10)", 
                  "  rho    ~ normal(0.5, 0.5)")

nc <- 4
o_SEIR <- write_SEIR_model("sym", filename, stock_list, params_prior,
                           pop_size, scenario = "underreporting",
                           nc = nc, recovery_time = 1.5 /7,
                           latent_period = 1.5 / 7)

wide_flu_data <- raw_data[-1, ]

stan_d <- list(n_obs    = length_data,
               n_difeq  = length(stock_list), # number of differential equations
               t0       = 0,
               ts       = 1:length_data,
               n_params = (1 + nc) * (nc / 2),
               y1       = pull(wide_flu_data, `00-04`),
               y2       = pull(wide_flu_data, `05-14`),
               y3       = pull(wide_flu_data, `15-44`),
               y4       = pull(wide_flu_data, `45+`))

arg_list <- list(data   = NULL, 
                 chains = 4,
                 warmup = 1000, 
                 iter   = 1000, 
                 cores  = 4,
                 seed   = 97268, 
                 refresh = 5)

arg_list$data    <- stan_d
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache            <- TRUE
cache_file           <- str_glue("./object_fits/Stan/flu57.rds")
output               <- run_stan(filename, var_cache, cache_file, arg_list)
flu_fit              <- output$stan_fit
```

### Trace plots

```{r}
indexes <- str_replace(o_SEIR$params, "k", "")

params_translation <- data.frame(
  original = str_glue("params[{1:10}]"),
  new      = str_glue("kappa[{indexes}]"))

color_scheme_set("purple")
posterior  <- rstan::extract(flu_fit, inc_warmup = TRUE, permuted = FALSE)
post_names <- dimnames(posterior)[[3]]

post_names[match(params_translation$original, post_names)] <- params_translation$new
dimnames(posterior)[[3]] <- post_names

mcmc_trace(posterior, pars = c("rho", params_translation$new),
           facet_args = list(labeller = label_parsed),
           n_warmup = 1000) +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text = element_text(size = 8))
```

### Fit

```{r}
source("./R/summarise_results.R")
source("./R/graphs.R")
posterior_df <- as.data.frame(flu_fit)
sim_data     <- extract_incidences(posterior_df, age_groups)

real_data    <- flu_data %>% filter(time != 0)

g_ts <- g_compare_ts(sim_data, real_data, intervals = TRUE, 
                     xlabel = "Week number")

real_data2 <- mutate(real_data, source = "syn data")

metrics <- accuracy_metrics(sim_data, real_data2, age_groups)

ggsave(file = "./plots/C_flu1957.pdf", g_ts, dpi = "print",
       height = 4, width = 6)
g_ts
```

### K matrix

```{r, fig.height = 4, fig.width = 4, fig.align = "center"}
source("./R/matrix_utils.R")
source('./R/summaries_utils.R')
cm                      <- get_cm_sym(4)
samples                 <- rstan::extract(flu_fit)
param_samples           <- samples$params
colnames(param_samples) <- o_SEIR$params

k_hat  <- get_mean_k_hat(param_samples, cm, nc, age_groups)
int_df <- get_k_intervals(param_samples, cm)

draw_WAIFW(k_hat, "Weekly rates", int_df, precision = 1)
```

### $R_0$

```{r}
specs_list <- list(x_pos = 2.04, ypos_mean = 17, ypos_median = 16,
                   text_size = 2, ypos_interval = 15,
                   title = "Symmetric matrix", xlabel = "")

R_0_obj <- posterior_R0(param_samples, cm, pop_df, tau_I = 1.5 / 7)

R_0_obj$g
```





