---
title: "Appendix B"
output:
  pdf_document: 
    number_sections: true
  html_notebook: default
header-includes:
  - \usepackage{booktabs}
---

This appendix aims to illustrate the sensitivity analysis performed on the 
calibration of disaggregated SEIR models to synthetic data via Hamiltonian Monte
Carlo. The sole assumption for the transmission rates lies in its symmetry. No
further constrains are imposed. The analysis is divided into two sections: 
1) Sensitivity to the population size; 2) Sensitivity to the number of cohorts.

\tableofcontents 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      cache = TRUE)

## WORKAROUND: https://github.com/rstudio/rstudio/issues/6692
## Revert to 'sequential' setup of PSOCK cluster in RStudio Console on macOS and R 4.0.0
if (Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) && 
    Sys.info()["sysname"] == "Darwin" && getRversion() == "4.0.0") {
  parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
}
```

```{r}
library(cmdstanr)
library(deSolve)
library(dplyr)
library(GGally)
library(ggalt)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(Metrics)
library(purrr)
library(readsdr)
library(reshape2)
library(rstan)
library(scales)
library(socialmixr)
library(stringr)
library(tictoc)
library(tidyr)

source("./R/graphs.R")
source("./R/Metrics.R")
source("./R/summaries_utils.R")
source("./R/synthetic_incidence.R")
```

\newpage

# Sensitivity to population size

## Scenarios

1. N = 10,000
2. N = 100,000
3. N = 1,000,000

```{r}
source("./R/synthetic_params.R")

case_names       <- c("10k", "100k", "1M")
pop_sizes        <- 10 ** (4:6)
names(pop_sizes) <- case_names

age_limits <- c(0, 5, 15, 45)

output_sp_list <- lapply(pop_sizes, produce_synthetic_params, 
                         age_limits = age_limits)
```


## Synthetic K matrix

For all population scenarios.

```{r}
# Symmetrical matrix
conceptual_matrix_sym <- c("k11", "k12", "k13", "k14",
                           "k12", "k22", "k23", "k24",
                           "k13", "k23", "k33", "k34",
                           "k14", "k24", "k34", "k44")

actual_K <- output_sp_list[[1]]$K_matrix

grey_actual_K <- output_sp_list[[1]]$g_K_matrix +
  scale_fill_gradient(low = "#D3D3D3", high = "#696969") +
  labs(subtitle = "Actual K")

output_sp_list[[1]]$g_K_matrix
```
\newpage

## Synthetic incidences

All incidences are underreported, where the reporting fraction is equal to 0.8

```{r}
seed               <- 49732
stop_time          <- 50
reporting_fraction <- 0.8
length_data        <- stop_time

output_gsi <- lapply(output_sp_list, generate_synthetic_incidence,
                     stop_time = stop_time, 
                     reporting_fraction = reporting_fraction,
                     seed = seed)
names(output_gsi) <- case_names
```

```{r, fig.height = 6}
combined_df <- imap_dfr(output_gsi, function(syn_obj, label) {
  syn_obj$tidy_list$und %>% mutate(case = label)
}) %>% mutate(case = factor(case, levels = case_names))

ggplot(combined_df, aes(x = time, y = y)) +
  geom_col(fill = "steelblue") +
  scale_y_continuous(labels = comma) +
  facet_grid(case ~ cohort, scales = "free") +
  theme_pubr() +
  labs(title = "Incidence per age group and scenario",
       y = "Incidence [cases / day]",
       x = "Days")
```
\newpage

## Calibration 

```{r params_Stan_und}
source("./R/stan_utils.R")
source("./R/write_SEIR_model.R")
source("./R/summarise_results.R")

n_warm_up <- 1000
n_iter    <- 1000
n_chains  <- 4
mtx       <- "sym"

arg_list_outline <- list(fit    = NULL,
                         data   = NULL, 
                         chains = n_chains,
                         warmup = n_warm_up, 
                         iter   = n_iter, 
                         cores  = 4,
                         seed   = NULL, 
                         refresh = 5)

stan_d_outline <- list(n_obs    = length_data,
                       n_params = 10,
                       n_difeq  = 20, # number of differential equations
                       y1       = NULL,
                       y2       = NULL,
                       y3       = NULL,
                       y4       = NULL,
                       t0       = 0,
                       ts       = 1:length_data)

params_prior <- c("  params ~ normal(0, 10)", 
                  "  rho    ~ normal(0.5, 0.5)")

# Sensitivity summary
sens_summary         <- vector(mode = "list", length(case_names))
names(sens_summary)  <- case_names

stan_fit_list     <- vector(mode = "list", length(case_names))
names(stan_fit_list)  <- case_names

time_sens         <- vector(mode = "list", length(case_names))
names(time_sens)  <- case_names
```


### Population size (N = 10,000)

```{r}
case     <- "10k"
filename <- str_glue("./Stan_files/Sens_analysis/Sens_{case}.stan")

par_pop <- output_gsi[[case]]$const_list$population
o_SEIR  <- write_SEIR_model(mtx, filename, output_gsi[[case]]$stock_list, 
                           params_prior, pop_size = par_pop, "underreporting")

stan_d    <- stan_d_outline

und_data  <- output_gsi[[case]]$data_list$und
stan_d$y1 <- und_data[[1]]
stan_d$y2 <- und_data[[2]]
stan_d$y3 <- und_data[[3]]
stan_d$y4 <- und_data[[4]]

seed             <- 571156516
arg_list         <- arg_list_outline
arg_list$data    <- stan_d
arg_list$seed    <- seed
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache             <- TRUE
cache_file            <- str_glue("./object_fits/Stan/Sens_analysis/stan_fit_{case}.rds")
output                <- run_stan(filename, var_cache, cache_file, arg_list)
stan_fit_list[[case]] <- output$stan_fit
time_sens[[case]]     <- output$time
```

```{r, fig.height = 2.5, fig.width = 5.5, fig.align = 'center'}
specs_list <- list(x_pos = 2.32, ypos_mean = 20, ypos_median = 17,
                   text_size = 2, ypos_interval = 14,
                   title = "Symmetric matrix", xlabel = "")


sens_summary[[case]] <- summarise_results(stan_fit_list[[case]], 
                                          conceptual_matrix_sym,
                                          output_gsi[[case]]$tidy_list$und, 
                                          output_sp_list[[case]]$population, 
                                          specs_list, 
                                          o_SEIR$params, actual_K,
                                          scenario = "underreporting")

pred_K <- sens_summary[[case]]$summary_k$g_k_hat + 
  labs(subtitle = "Predicted K")

grid.arrange(pred_K, grey_actual_K, ncol = 2)
```

\hfill

```{r fig.height = 3.5, fig.align = 'center'}
sens_summary[[case]]$ts_summary$g_comparison
```


### Population size (N = 100,000)

```{r}
case     <- "100k"
filename <- str_glue("./Stan_files/Sens_analysis/Sens_{case}.stan")

par_pop <- output_gsi[[case]]$const_list$population
o_SEIR  <- write_SEIR_model(mtx, filename, output_gsi[[case]]$stock_list, 
                           params_prior, pop_size = par_pop, "underreporting")

stan_d    <- stan_d_outline

und_data  <- output_gsi[[case]]$data_list$und
stan_d$y1 <- und_data[[1]]
stan_d$y2 <- und_data[[2]]
stan_d$y3 <- und_data[[3]]
stan_d$y4 <- und_data[[4]]

seed             <- 33130451
arg_list         <- arg_list_outline
arg_list$data    <- stan_d
arg_list$seed    <- seed
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache             <- TRUE
cache_file            <- str_glue("./object_fits/Stan/Sens_analysis/stan_fit_{case}.rds")
output                <- run_stan(filename, var_cache, cache_file, arg_list)
stan_fit_list[[case]] <- output$stan_fit
time_sens[[case]]     <- output$time
```

```{r, fig.height = 2.5, fig.width = 5.5, fig.align = 'center'}
specs_list <- list(x_pos = 2.32, ypos_mean = 20, ypos_median = 17,
                   text_size = 2, ypos_interval = 14,
                   title = "Symmetric matrix", xlabel = "")


sens_summary[[case]] <- summarise_results(stan_fit_list[[case]], 
                                          conceptual_matrix_sym,
                                          output_gsi[[case]]$tidy_list$und, 
                                          output_sp_list[[case]]$population, 
                                          specs_list, 
                                          o_SEIR$params, actual_K,
                                          scenario = "underreporting")

pred_K <- sens_summary[[case]]$summary_k$g_k_hat + 
  labs(subtitle = "Predicted K")

grid.arrange(pred_K, grey_actual_K, ncol = 2)
```

\hfill

```{r fig.height = 3.5, fig.align = 'center'}
sens_summary[[case]]$ts_summary$g_comparison
```

### Population size (N = 1,000,000)

```{r}
case     <- "1M"
filename <- str_glue("./Stan_files/Sens_analysis/Sens_{case}.stan")

par_pop <- output_gsi[[case]]$const_list$population
o_SEIR  <- write_SEIR_model(mtx, filename, output_gsi[[case]]$stock_list, 
                           params_prior, pop_size = par_pop, "underreporting")

stan_d    <- stan_d_outline

und_data  <- output_gsi[[case]]$data_list$und
stan_d$y1 <- und_data[[1]]
stan_d$y2 <- und_data[[2]]
stan_d$y3 <- und_data[[3]]
stan_d$y4 <- und_data[[4]]

seed             <- 9207491
arg_list         <- arg_list_outline
arg_list$data    <- stan_d
arg_list$seed    <- seed
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache             <- TRUE
cache_file            <- str_glue("./object_fits/Stan/Sens_analysis/stan_fit_{case}.rds")
output                <- run_stan(filename, var_cache, cache_file, arg_list)
stan_fit_list[[case]] <- output$stan_fit
time_sens[[case]]     <- output$time
```

```{r, fig.height = 2.5, fig.width = 5.5, fig.align = 'center'}
specs_list <- list(x_pos = 2.32, ypos_mean = 20, ypos_median = 17,
                   text_size = 2, ypos_interval = 14,
                   title = "Symmetric matrix", xlabel = "")


sens_summary[[case]] <- summarise_results(stan_fit_list[[case]], 
                                          conceptual_matrix_sym,
                                          output_gsi[[case]]$tidy_list$und, 
                                          output_sp_list[[case]]$population, 
                                          specs_list, 
                                          o_SEIR$params, actual_K,
                                          scenario = "underreporting")

pred_K <- sens_summary[[case]]$summary_k$g_k_hat + 
  labs(subtitle = "Predicted K")

grid.arrange(pred_K, grey_actual_K, ncol = 2)
```

\hfill

```{r fig.height = 3.5, fig.align = 'center'}
sens_summary[[case]]$ts_summary$g_comparison
```
## Reporting value

```{r, fig.height = 4}

rv_stan  <- map_df(sens_summary, function(sum_stan) {
  rho_list <- sum_stan$rho_hat
  
  data.frame(y = rho_list$mean,
             lower.bound = rho_list$lower_bound,
             upper.bound = rho_list$upper_bound)
}) %>% mutate(x = factor(case_names, levels = case_names))

ggplot(rv_stan, aes(x = x, y = y)) +
    geom_point() +
    geom_errorbar(aes(ymin = lower.bound, ymax = upper.bound), width =.1) +
    geom_hline(yintercept = reporting_fraction, linetype = "dashed") +
    scale_y_continuous(limits = c(0.7, 0.9)) +
    theme_pubr() +
    theme(legend.text  = element_text(size = 3)) +
    labs(x = "Scenario", y = "Reporting fraction",
         title = "Reporting fraction by scenario",
         caption = "The dashed line indicates the actual value")
```

## $R_0$

```{r, fig.height = 4}
R0_df <- map_df(sens_summary, consolidate_R0) %>% 
  mutate(x = factor(case_names, levels = case_names))

ggplot(R0_df, aes(x = x, y = R0)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower.bound, ymax = upper.bound), width =.1) +
  geom_hline(yintercept = output_sp_list[[1]]$theoretical_R0, 
             linetype = "dashed") +
  scale_y_continuous(limits = c(2.2, 2.4)) +
  theme_pubr() +
  theme(legend.text  = element_text(size = 3)) +
  labs(x = "Scenario", y = bquote(R[0]),
       caption = "The dashed line indicates the actual value")
```

## Time comparison

```{r, fig.height = 5}
times <- map_dbl(time_sens, calculate_time)

time_df <- data.frame(x = pop_sizes, y = times)

ggplot(time_df, aes(x = x, y = y)) +
  geom_lollipop(colour = "steelblue") +
  geom_line(colour = "grey30", alpha = 0.5, linetype = "dotted") +
  scale_x_log10(labels = comma) +
  theme_pubr() +
  labs(x = "Population size",
       y = "Time [Minutes]",
       title = "Run time per scenario")
```


\newpage

# Sensitivity to the number of cohorts

## Scenarios

1. n = 4
2. n = 5
3. n = 6

```{r}
case_names         <- c("n4", "n5", "n6")
n_coh              <- 4:6
names(n_coh)       <- case_names
pop_size           <- 1e5
stop_time          <- 50
reporting_fraction <- 0.8
length_data        <- stop_time

source("./R/matrix_utils.R")
cm_list    <- lapply(n_coh, get_cm_sym)
case_names -> names(cm_list)
```

## K matrices

```{r, fig.height = 7, fig.width = 5}
age_limits_list <- list(c(0, 5, 15, 45),
                        c(0, 5, 10, 15, 45),
                        c(0, 5, 10, 15, 20, 45))

names(age_limits_list) <- case_names

output_sp_list  <- lapply(age_limits_list, function(age_limits, pop_size){
  produce_synthetic_params(pop_size, age_limits)
}, pop_size = pop_size)

titles <- paste0("n = ", n_coh)

g_K_matrix_list <- purrr::map(output_sp_list, "g_K_matrix") %>% 
  map2(titles, function(g_obj, title) {
    g_obj + labs(subtitle = title)
  })

grey_K_list <- lapply(output_sp_list, function(output_sp) {
  output_sp$g_K_matrix +
  scale_fill_gradient(low = "#D3D3D3", high = "#696969") +
  labs(subtitle = "Actual K")
})

do.call("grid.arrange", c(g_K_matrix_list, ncol = 1))
```

## $R0$

```{r}
actual_R0 <- data.frame(x  = case_names,
                        R0 = map_dbl(output_sp_list, "theoretical_R0"))
```

1. For n = 4, `r round(actual_R0[[1, 2]], 2)`
1. For n = 5, `r round(actual_R0[[2, 2]], 2)`
1. For n = 6, `r round(actual_R0[[3, 2]], 2)`

## Synthetic incidences

```{r}
seed       <- 648717
output_gsi <- lapply(output_sp_list, generate_synthetic_incidence,
                     stop_time = stop_time, 
                     reporting_fraction = reporting_fraction,
                     seed = seed)
```

```{r}
df <- output_gsi[[1]]$tidy_list$und

ggplot(df, aes(x = time, y = y)) +
  geom_col(fill = "steelblue") +
  facet_wrap(~cohort) +
  theme_pubr() +
  labs(title    = "Incidence per age group and scenario",
       subtitle = "n = 4",
       x        = "Days",
       y        = "Incidence")
```

```{r}
df <- output_gsi[[2]]$tidy_list$und

ggplot(df, aes(x = time, y = y)) +
  geom_col(fill = "steelblue") +
  facet_wrap(~cohort) +
  theme_pubr() +
  labs(title = "Incidence per age group and scenario",
       subtitle = "n = 5",
       x        = "Days",
       y        = "Incidence")
```

```{r}
df <- output_gsi[[3]]$tidy_list$und

ggplot(df, aes(x = time, y = y)) +
  geom_col(fill = "steelblue") +
  facet_wrap(~cohort) +
  theme_pubr() +
  labs(title = "Incidence per age group and scenario",
       subtitle = "n = 6",
       x        = "Days",
       y        = "Incidence")
```



## Calibration

```{r cal_coh}
source("./R/stan_utils.R")
source("./R/write_SEIR_model.R")
source("./R/summarise_results.R")

n_warm_up <- 1000
n_iter    <- 1000
n_chains  <- 4
mtx       <- "sym"

arg_list_outline <- list(fit    = NULL,
                         data   = NULL, 
                         chains = n_chains,
                         warmup = n_warm_up, 
                         iter   = n_iter, 
                         cores  = 4,
                         seed   = NULL, 
                         refresh = 5)

params_prior <- c("  params ~ normal(0, 10)", 
                  "  rho    ~ normal(0.5, 0.5)")

# Sensitivity to number of cohorts summary
sens_coh_summary        <- vector(mode = "list", length(case_names))
names(sens_coh_summary) <- case_names

coh_fit_list        <- vector(mode = "list", length(case_names))
names(coh_fit_list) <- case_names

time_coh        <- vector(mode = "list", length(case_names))
names(time_coh) <- case_names
```

### 4 Cohorts

```{r}
coh <- "n4"
nc  <- n_coh[[coh]]


y_list        <- output_gsi[[coh]]$data_list$und
names(y_list) <- paste0("y", 1:length(y_list))

stan_d <- c(list(n_obs    = length_data,
                 n_difeq  = length(output_gsi[[coh]]$stock_list), # number of differential equations
                 t0       = 0,
                 ts       = 1:length_data),
                 n_params = (1 + nc) * (nc / 2),
                 y_list)

filename     <- str_glue("./Stan_files/Sens_analysis/{nc}_cohorts.stan")

o_SEIR <- write_SEIR_model(mtx, filename, output_gsi[[coh]]$stock_list, 
                                 params_prior, pop_size = pop_size, 
                                 "underreporting", n = nc)

seed             <- 478219
arg_list         <- arg_list_outline
arg_list$data    <- stan_d
arg_list$seed    <- seed
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache            <- TRUE
cache_file           <- str_glue("./object_fits/Stan/stan_fit_und_{nc}n_{mtx}.rds")
output               <- run_stan(filename, var_cache, cache_file, arg_list)
coh_fit_list[[coh]]  <- output$stan_fit
time_coh[[coh]]      <- output$time
```

```{r, fig.height = 2.5, fig.width = 5.5, fig.align = 'center'}
specs_list <- list(x_pos = 2.32, ypos_mean = 20, ypos_median = 17,
                   text_size = 2, ypos_interval = 14,
                   title = "Symmetric matrix", xlabel = "")


sens_coh_summary[[coh]] <- summarise_results(coh_fit_list[[coh]],
                                             cm_list[[coh]],
                                             output_gsi[[coh]]$tidy_list$und, 
                                             output_sp_list[[coh]]$population, 
                                             specs_list, 
                                             o_SEIR$params, 
                                             output_sp_list[[coh]]$K_matrix,
                                             scenario = "underreporting")

pred_K <- sens_coh_summary[[coh]]$summary_k$g_k_hat + 
  labs(subtitle = "Predicted K")

grid.arrange(pred_K, grey_K_list[[coh]], ncol = 2)
```

\hfill

```{r fig.height = 3.5, fig.align = 'center'}
sens_coh_summary[[coh]]$ts_summary$g_comparison
```


### 5 Cohorts

```{r stan_fit_5_cohorts}
coh <- "n5"
nc  <- n_coh[[coh]]
filename     <- str_glue("./Stan_files/Sens_analysis/5_cohorts.stan")

o_SEIR <- write_SEIR_model(mtx, filename, output_gsi[[coh]]$stock_list, 
                           params_prior, pop_size = pop_size, 
                           "underreporting", n = nc)

y_list        <- output_gsi[[coh]]$data_list$und
names(y_list) <- paste0("y", 1:length(y_list))

stan_d <- c(list(n_obs    = length_data,
                 n_difeq  = length(output_gsi[[coh]]$stock_list), # number of differential equations
                 t0       = 0,
                 ts       = 1:length_data),
                 n_params = (1 + nc) * (nc / 2),
                 y_list)

seed             <- 241364
arg_list         <- arg_list_outline
arg_list$data    <- stan_d
arg_list$seed    <- seed
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache            <- TRUE
cache_file           <- str_glue("./object_fits/Stan/stan_fit_und_5n_{mtx}.rds")
output               <- run_stan(filename, var_cache, cache_file, arg_list)
coh_fit_list[[coh]]  <- output$stan_fit
time_coh[[coh]]      <- output$time
```

```{r, fig.height = 3, fig.width = 6, fig.align = 'center'}
specs_list <- list(x_pos = 2.32, ypos_mean = 20, ypos_median = 17,
                   text_size = 2, ypos_interval = 14,
                   title = "Symmetric matrix", xlabel = "")


sens_coh_summary[[coh]] <- summarise_results(coh_fit_list[[coh]],
                                             cm_list[[coh]],
                                             output_gsi[[coh]]$tidy_list$und, 
                                             output_sp_list[[coh]]$population, 
                                             specs_list, 
                                             o_SEIR$params, 
                                             output_sp_list[[coh]]$K_matrix,
                                             scenario = "underreporting")

pred_K <- sens_coh_summary[[coh]]$summary_k$g_k_hat + 
  labs(subtitle = "Predicted K")

grid.arrange(pred_K, grey_K_list[[coh]], ncol = 2)
```

\hfill

```{r fig.height = 3.5, fig.align = 'center'}
sens_coh_summary[[coh]]$ts_summary$g_comparison
```

### 6 Cohorts

```{r}
coh <- "n6"
nc  <- n_coh[[coh]]


y_list        <- output_gsi[[coh]]$data_list$und
names(y_list) <- paste0("y", 1:length(y_list))

stan_d <- c(list(n_obs    = length_data,
                 n_difeq  = length(output_gsi[[coh]]$stock_list), # number of differential equations
                 t0       = 0,
                 ts       = 1:length_data),
                 n_params = (1 + nc) * (nc / 2),
                 y_list)

filename     <- str_glue("./Stan_files/Sens_analysis/{nc}_cohorts.stan")

o_SEIR <- write_SEIR_model(mtx, filename, output_gsi[[coh]]$stock_list, 
                                 params_prior, pop_size = pop_size, 
                                 "underreporting", n = nc)

seed             <- 102156
arg_list         <- arg_list_outline
arg_list$data    <- stan_d
arg_list$seed    <- seed
arg_list$data$y0 <- o_SEIR$stock_inits

var_cache            <- TRUE
cache_file           <- str_glue("./object_fits/Stan/stan_fit_und_{nc}n_{mtx}.rds")
output               <- run_stan(filename, var_cache, cache_file, arg_list)
coh_fit_list[[coh]]  <- output$stan_fit
time_coh[[coh]]      <- output$time
```

```{r, fig.height = 3.25, fig.width = 6.5, fig.align = 'center'}
specs_list <- list(x_pos = 2.32, ypos_mean = 20, ypos_median = 17,
                   text_size = 2, ypos_interval = 14,
                   title = "Symmetric matrix", xlabel = "")


sens_coh_summary[[coh]] <- summarise_results(coh_fit_list[[coh]],
                                             cm_list[[coh]],
                                             output_gsi[[coh]]$tidy_list$und, 
                                             output_sp_list[[coh]]$population, 
                                             specs_list, 
                                             o_SEIR$params, 
                                             output_sp_list[[coh]]$K_matrix,
                                             scenario = "underreporting")

pred_K <- sens_coh_summary[[coh]]$summary_k$g_k_hat + 
  labs(subtitle = "Predicted K")

grid.arrange(pred_K, grey_K_list[[coh]], ncol = 2)
```

\hfill

```{r fig.height = 3.5, fig.align = 'center'}
sens_coh_summary[[coh]]$ts_summary$g_comparison
```

## Reporting value

```{r, fig.height = 4}

rv_stan  <- map_df(sens_coh_summary, function(sum_stan) {
  rho_list <- sum_stan$rho_hat
  
  data.frame(y = rho_list$mean,
             lower.bound = rho_list$lower_bound,
             upper.bound = rho_list$upper_bound)
}) %>% mutate(x = factor(case_names, levels = case_names))

ggplot(rv_stan, aes(x = x, y = y)) +
    geom_point() +
    geom_errorbar(aes(ymin = lower.bound, ymax = upper.bound), width =.1) +
    geom_hline(yintercept = reporting_fraction, linetype = "dashed") +
    scale_y_continuous(limits = c(0.7, 0.9)) +
    theme_pubr() +
    theme(legend.text  = element_text(size = 3)) +
    labs(x = "Scenario", y = "Reporting fraction",
         title = "Reporting fraction by scenario")
```

## Estimated $R_0$

```{r, fig.height = 4}
R0_df <- map_df(sens_coh_summary, consolidate_R0) %>% 
  mutate(x = factor(case_names, levels = case_names))

ggplot(R0_df, aes(x = x, y = R0)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_errorbar(aes(ymin = lower.bound, ymax = upper.bound), width =.1, 
                alpha = 0.75) +
  scale_y_continuous(limits = c(2.25, 2.38)) +
  geom_point(data = actual_R0, colour = "red", alpha = 0.5, size = 2, 
             shape = 4) +
  theme_pubr() +
  theme(legend.text  = element_text(size = 3)) +
  labs(x = "Scenario", y = bquote(R[0]),
       caption = "The cross indicates the actual value",
       title = "Estimation per scenario")
```


## Time comparison

```{r}
times <- map_dbl(time_coh, calculate_time)

time_df <- data.frame(x = n_coh, y = times)

ggplot(time_df, aes(x = x, y = y)) +
  geom_lollipop(colour = "steelblue") +
  geom_line(colour = "grey30", alpha = 0.5, linetype = "dotted") +
  scale_x_continuous(breaks = 4:6) +
  theme_pubr() +
  labs(x = "Number of cohorts",
       y = "Time [Minutes]",
       title = "Run time per scenario")
```


# Original Computing Environment

```{r}
sessionInfo()
```
